---
title: "Palmetto Binary Logistic Regression"
author: "Anastasia Kunz"
date: "2/2/2021"
output:
  html_document
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)


```



```{r}
palmetto <- read_csv(here("data", "palmetto.csv"),
                     col_types = cols(.default = 'c')) %>% 
  mutate(height = as.numeric(height)) %>% 
  mutate(length = as.numeric(length)) %>% 
  mutate(width = as.numeric(width)) %>% 
  mutate(green_lvs = as.numeric(green_lvs))
```

### Data Visualizations

2-3 finalized data visualizations with fig capts exploring differeences in height canopy length, canopy width, and green leaves for the two species

below each visualization add a short (1 sentence) statement on the takeaway

```{r}
palmetto_subset <- palmetto %>% 
  select(species, height, length, width, green_lvs)
```


height

```{r}
ggplot(data = palmetto_subset, aes(x = height))+
  geom_histogram()+
  facet_wrap(~ species)

ggplot(data = palmetto_subset, aes(x = species, y = height))+
  geom_boxplot()
```

```{r}
ggplot(data = palmetto_subset, aes(x = length))+
  geom_histogram()+
  facet_wrap(~ species)

ggplot(data = palmetto_subset, aes(x = species, y = length))+
  geom_boxplot()
```


```{r}
ggplot(data = palmetto_subset, aes(x = width))+
  geom_histogram()+
  facet_wrap(~ species)

ggplot(data = palmetto_subset, aes(x = species, y = width))+
  geom_boxplot()
```



```{r}
ggplot(data = palmetto_subset, aes(x = green_lvs))+
  geom_histogram()+
  facet_wrap(~ species)

ggplot(data = palmetto_subset, aes(x = species, y = green_lvs))+
  geom_boxplot()
```



#### binary logistic regression

using plant height, canopy length, canopy width, and green leaves as predictor variables to understand how they can relate to probability of a plant being Serenoa repens or Sabal etonia


#### Section evaluating how successful this mdel is

how successfully can it classify a plant as the correct species using a 50% cutoff

make finalized table


### Citation

Abrahamson, W.G. 2019. Survival, growth and biomass estimates of two dominant palmetto species of south-central Florida from 1981 - 2017, ongoing at 5-year intervals ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/f2f96ec76fbbd4b9db431c79a770c4d5






